IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-04-24 paper/rebuttal.txt

We would like to thank all reviewers for their feedback and suggestions.  We will first reply to high-level comments and then reply to specific questions in the reviews.

High-level comments
-------------------

Several reviewers raised questions about the generality as well as the practical scalability of our approach, in particular with regards to external effects.  We note that as a first step our framework assumes the target language to be free of external effects.  The problem of adding IFC even to such languages is non-trivial and error-prone (e.g., see [29]).  Furthermore, some practical languages like ECMAScript are of this form, and external effects such as XMLHttpRequest are added as extensions to it in browsers to arrive at JavaScript.
Devising a general mechanism to deal with external effects is challenging and requires a formal definition of the external effects, which can vary widely across systems.  Soundly dealing with such external effects requires these effects to be internalized into the IFC language, and for XMLHttpRequest in SWAPI we show how do exactly that.

Another point raised by the reviewers is the missing connection between the real-world examples and the formal framework, and that it feels like we are trying to shoe-horn two previous one-off retrofittings into a unified framework.  This is not the case, in fact, the cause-and-effect relationship is the other way around.  The general framework for IFC presented in this paper has influenced both SWAPI as well as LIO, helping to decide what a non-interfering implementation needs to provide.  For example, mumble mumble exceptions.

Reviewer 1 asks about the extension section, and whether these are speculative ideas or not.  Extensions to the IFC language are largely orthogonal to the core contribution of combining coarse-grained IFC with a target language.  To keep the presentation in earlier clean of orthogonal distractions, we only present more advanced IFC features in the extension section.  However, these extensions have been worked out, and are also part of the JavaScript or Haskell implementation, or both.
W.r.t. the comment about labeled references not being amenable to Matthews-Findler-style semantics, we note that in a coarse-grained approach like ours, the labeled references are part of the IFC state and the references are distinct from the native references a target language might have.  For this reason, there is no conflict with the approach of Matthews and Findler.

Specific questions
------------------

Reviewer 1 ask why we have not developed our formalism with a monad.  One of our motivations was to formalize an IFC system for JavaScript, whose semantics are typically not presented in a stratified way by distinguishing a monadic and a pure fragment.  A non-monadic approach enables a more natural formalism for a large class of languages, including JavaScript.

Reviewer 2 ask about the proof strategy for Theorem 3.  Performing induction on the length of the derivation sequence followed by induction on the derivation tree is standard for small-step operational semantics.  This is isomorphic to induction on the structure of the derivation for ->*.

Reviewer 1 ask about the soundness of the JS-send rule.  While omitted in the paper, this rule can be proven to be non-interfering.  Intuitively, for an attacker at level L, the additional premise evaluates regardless of secrets at a level above L, thus ensuring that no secrets can be observed.

Reviewer 2 correctly points out that on page 6 the second \Sigma_1 in c_1 should be \Sigma_2.

Reviewer 3 asks about shared mutable references:  It is correct that a different design choice might allow shared mutable references in this way.  However, because native references are protected by the current label, this would effectively be a fine-grained IFC system, requiring checks for all reference reads and writes.  This would be against our goal of a coarse-grained system.  We will improve the unfortunate phrase in our paper.

Reviewer 3 asks about the values sent across channels in SWAPI.  For simplicity, we require them to be strings in the paper, thought any structurally cloned object (as well as labeled blobs) are allowed in the actual implementation.

As reviewer 3 points out, the reference about SWAPI does not include an URL.  It is available at http://deian.net/swapi.pdf and currently not indexed by search engines because the paper is under anonymous review.  We apologize for the mistake.

### 2014-04-25 paper/rebuttal.txt

# Generality and novelty of the system

A reviewer raised the question of the generality of the framework and
asks how does our work scales in practice -- indeed if there is clear
path to retrofitting real languages with IFC or did we just shoe-horn
SWAPI and LIO into a "unified framework".

First, we note that our framework assumes that the target language
must not have external effects. In section 6 we show how real-world
languages can be constrained to achieve this. For C we use Dune, for
Haskell we use types, and for browser-JS we use CSP. Unfortunately due
to space restrictions we left the discussion of the mapping to the
formalism as informal discussion (doing this at the cost of section 8
seems natural).

We do not claim that our work is general enough to handle languages
where effects cannot be tamed (we will emphasize this on revision).
Yet some languages can be tamed (as we discuss) and others don't even
have external effects.  For example, our work is directly applicable
to "vanilla" JS (EcmaScript), which does not have any external effects
-- indeed, under one lens, one can see our work as presenting an
alternative (to [25]) IFC semantics for JS.  Indeed the motivation
behind this work was to address the question of how to build an
efficient, non-intrusive IFC system for JS.

While our language uses ideas from LIO and SWAPI, we note that the
current (and at the time of the writing) versions of these systems are
using the concepts of this paper. It is not the case that "the
framework didn't come first". For instance, in LIO [53] (and Breeze
[28]) exceptions were original treated in a rather complex fashion; as
we discuss in the paper, exceptions are internal effects and thus the
security concern becomes trivial; LIO now uses this approach (and
regular Haskell exceptions vs. labeled exceptions).

Addressing the first reviewer's concern that the IFC system presented
is a rehash prior work, we remark that this approach of dealing with
internal effects and our asynchronous communication primitives is
novel. Moreover, we believe that the formalization serves as a
stepping stone for reasoning about IFC OS work.

# Extensions

The reviewers asked if we actually worked out the extensions to
language. We chose to present the core ideas separate from extensions
for simplicity and because the features largely depend on the
embedding. For example, labeled MVars are natural to Haskell, but
not JS. Nevertheless, these extensions have been formalized and are
implemented in LIO and/or SWAPI. (The only extension common
to both system systems are labeled values.) The main points on how
to extend the system with such features follows from the discussion:
they must be added to the IFC language and the no sharing
"sandbox-local pointers" rule (of send) must be used.  For example,
in the labeled references case we amend the IFC language state to
contain a labeled reference store; these labeled references are
distinct from the native references a target language might have and
all access abides by IFC.  (For this reason, there is also no
conflict with the approach of Matthews and Findler as brought up by
the first reviewer.)

# External effects

The reviewers are concerned that our treatment of external effects
makes the work incomplete. We remark that like other IFC systems [A
XXXX Z], external effects can be handled by internalizing them into
the IFC language. In practice and as in the XMLHttpRequest (as used in
SWAPI) case this amounts to wrapping the "native" unsafe code. While
we can extend the language with a general external effect primitive
(e.g., 'out') we do not think this add much value, formally or
practically. Finally, and most importantly, the treatment of external
effects is very much application specific. For instance, the HTTP
client in SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both
wrap the native code with label checks, but the semantics differ
(simply because of the different use cases: browser vs. server).
While important for (certain) practical applications, we believe that
general treatment of such effects is an open problem and complementary
to this work.

# Other questions

Reviewer 3 asks about shared mutable references:  It is correct that a
different design choice might allow shared mutable references in this
way.  However, because native references are protected by the current
label, this would effectively be a fine-grained IFC system, requiring
checks for all reference reads and writes.  This would be against our
goal of a coarse-grained system.  We will improve the unfortunate
phrasing.

Reviewer 3 asks about the values sent across channels in SWAPI.  For
simplicity, we require them to be strings in the paper, thought any
structurally cloned object (as well as labeled blobs) are actually
permitted.

@@

Reviewer 1 ask why we have not developed our formalism with a monad.
One of our motivations was to formalize an IFC system for JavaScript,
whose semantics are typically not presented in a stratified way by
distinguishing a monadic and a pure fragment.  A non-monadic approach
enables a more natural formalism for a large class of languages,
including JavaScript.

Reviewer 2 ask about the proof strategy for Theorem 3.  Performing
induction on the length of the derivation sequence followed by
induction on the derivation tree is standard for small-step
operational semantics.  This is isomorphic to induction on the
structure of the derivation for ->*.

Reviewer 1 ask about the soundness of the JS-send rule.  While omitted
in the paper, this rule can be proven to be non-interfering.
Intuitively, for an attacker at level L, the additional premise
evaluates regardless of secrets at a level above L, thus ensuring that
no secrets can be observed.

As reviewer 3 points out, the reference about SWAPI does not include
an URL.  It is available at http://deian.net/swapi.pdf and currently
not indexed by search engines because the paper is being anonymously
submitted.  We apologize for the mistake.

### 2014-04-25 paper/rebuttal.txt

# Generality and novelty of the system

A reviewer asked if our system really applies to real-world languages,
pointing to our inability to deal with external effects.  It is true
that our framework assumes that the target language must not have
external effects.  However, this is not an unreasonable constraint: in
Section 6, we discussed how real-world languages can be constrained to
achieve this.  Unfortunately due to space restrictions we left the
discussion of the mapping to the formalism as informal discussion (doing
this at the cost of section 8 seems natural).

@@

We do not claim that our work is general enough to handle languages
where effects cannot be tamed (we will emphasize this on revision).
Yet some languages can be tamed (as we discuss) and others don't even
have external effects.  For example, our work is directly applicable
to "vanilla" JS (EcmaScript), which does not have any external effects
-- indeed, under one lens, one can see our work as presenting an
alternative (to [25]) IFC semantics for JS.  Indeed the motivation
behind this work was to address the question of how to build an
efficient, non-intrusive IFC system for JS.

Similarly, there was a comment that this work simply shoe-horned SWAPI
and LIO into a "unified framework".  While our language uses ideas from
LIO and SWAPI, we note that the current (and at the time of the writing)
versions of these systems are using the concepts of this paper. It is
not the case that "the framework didn't come first". For instance, in
LIO [53] (and Breeze [28]) exceptions were originally treated in a rather
complex fashion; as we discuss in the paper, exceptions are internal
effects and thus the security concern becomes trivial; LIO was modified to
adopt this new approach.

As for the first reviewer's concern that the IFC system presented
is simply a rehash of prior work, we claim the approach of dealing with
internal effects and our asynchronous communication primitives is
novel. Moreover, we believe that the formalization serves as a
stepping stone for formal reasoning about IFC OS work.

### 2014-04-25 paper/rebuttal.txt

Generality and novelty of the system
------------------------------------

@@

A reviewer asked if our system really applies to real-world languages,
pointing to our inability to deal with external effects.  It is true
that our framework assumes that the target language must not have
external effects.  However, this is not an unreasonable constraint: in
Section 6, we discussed how real-world languages can be constrained to
achieve this.  Unfortunately due to space restrictions we left the
discussion of the mapping to the formalism as informal discussion (doing
this at the cost of section 8 seems natural).

We do not claim that our work is general enough to handle languages
where effects cannot be tamed (we will emphasize this on revision).
Yet some languages can be tamed (as we discuss) and others don't even
have external effects.  For example, our work is directly applicable
to "vanilla" JS (EcmaScript), which does not have any external effects
-- indeed, under one lens, one can see our work as presenting an
alternative (to [25]) coarse-grained IFC system for JS.  Indeed the
motivation behind this work was to address the question of how to
build an efficient, non-intrusive IFC system for JS.

@@

Similarly, there was a comment that this work simply shoe-horned SWAPI
and LIO into a "unified framework".  While our language uses ideas from
LIO and SWAPI, we note that the current (and at the time of the writing)
versions of these systems are using the concepts of this paper. It is
not the case that "the framework didn't come first". For instance, in
LIO [53] (and Breeze [28]) exceptions were originally treated in a rather
complex fashion; as we discuss in the paper, exceptions are internal
effects and thus the security concern becomes trivial; LIO was modified to
adopt this new approach.

As for the first reviewer's concern that the IFC system presented is
simply a rehash of prior work, we claim the approach of dealing with
internal effects and our asynchronous communication primitives is
novel. To our knowledge this is the first language-based dynamic IFC
system to use such asynchronous primitives and work on both concurrent
and sequential schedulers. (While simple, the checks performed by our
asynchronous communication primitives imply a more flexible
system---synchronous primitives effectively impose that the end-points
have the same label.) Moreover, we believe that our formalization
serves as a stepping stone for formal reasoning about IFC OS work.

Extensions
----------

@@

The reviewers asked if we actually worked out the extensions to
language. We chose to present the core ideas separate from extensions
for simplicity and because the features largely depend on the
embedding. For example, labeled MVars are natural to Haskell, but
not JS. Nevertheless, these extensions have been formalized and are
implemented in LIO and/or SWAPI. (The only extension common
to both system systems are labeled values.) The main points on how
to extend the system with such features follows from the discussion:
they must be added to the IFC language and the no sharing
"sandbox-local pointers" rule (of send) must be used.  For example,
in the labeled references case we amend the IFC language state to
contain a labeled reference store; these labeled references are
distinct from the native references a target language might have and
all access abides by IFC.  (For this reason, there is also no
conflict with the approach of Matthews and Findler as brought up by
the first reviewer.)

External effects
----------------

The reviewers are concerned that our treatment of external effects
makes the work incomplete. We remark that like other IFC systems [A
XXXX Z], external effects can be handled by internalizing them into
the IFC language. In practice and as in the XMLHttpRequest (as used in
SWAPI) case this amounts to wrapping the "native" unsafe code. While
we can extend the language with a general external effect primitive
(e.g., 'out') we do not think this add much value, formally or
practically. Finally, and most importantly, the treatment of external
effects is very much application specific. For instance, the HTTP
client in SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both
wrap the native code with label checks, but the actual label checks
differ simply because of the different setting and attacker models:
browser vs. server.  While important for (certain) practical
applications, we believe that general treatment of such effects is an
open problem and complementary to this work.

Other questions
---------------

### 2014-04-25 paper/rebuttal.txt

Extensions
----------

The reviewers asked if we actually worked out the extensions to
language. We chose to present the core ideas separate from extensions
for simplicity and because the features largely depend on the
embedding. For example, labeled MVars are natural to Haskell, but
not JS. Nevertheless, these extensions have been formalized and are
implemented in LIO and/or SWAPI. (The only extension common
to both system systems are labeled values.) The main points on how
to extend the system with such features follows from the discussion:
they must be added to the IFC language and the no sharing
"sandbox-local pointers" rule (of send) must be used.  For example,
in the labeled references case we amend the IFC language state to
contain a labeled reference store; these labeled references are
distinct from the native references a target language might have and
all access abides by IFC.  (For this reason, there is also no
conflict with the approach of Matthews and Findler as brought up by
the first reviewer.)

External effects
----------------

The reviewers are concerned that our treatment of external effects makes the
work incomplete. We remark that like other IFC systems, external effects can be
handled by internalizing them (manually) into the IFC language. For instance,
JPMail (a secure mail agent) [1] essentially re-implements the primitives with
external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
internalizes external effects by wrapping the corresponding primitives to be
IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
amounts to wrapping the "native" unsafe code. While we can extend the language
with a general external effect primitive (e.g., 'out'), we do not think this add
much value, formally or practically. This is because the treatment of external
effects is very much application specific. For instance, the HTTP client in
SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
to make IFC-aware, but the actual label checks differ simply because of the
different setting and attacker models: browser (client) vs. server.  While
important for pushing IFC into practice, we believe that general treatment of
external effects is an open problem and complementary to this work.

@@

Reviewer 3 asks about shared mutable references:  It is correct that a
different design choice might allow shared mutable references in this
way.  However, because native references are protected by the current
label, this would effectively be a fine-grained IFC system, requiring
checks for all reference reads and writes.  This would be against our
goal of a coarse-grained system.  We will improve the unfortunate
phrasing.

Reviewer 3 asks about the values sent across channels in SWAPI.  For
simplicity, we require them to be strings in the paper, thought any
structurally cloned object (as well as labeled blobs) are actually
permitted.

Reviewer 1 ask about the soundness of the JS-send rule.  While omitted
in the paper, this rule can be proven to be non-interfering.
Intuitively, for an attacker at level L, the additional premise
evaluates regardless of secrets at a level above L, thus ensuring that
no secrets can be observed.

References
----------

[1] Boniface Hicks, Kiyan Ahmadizadeh, and Patrick McDaniel. Understanding
practical application development in security-typed languages. In 22nd Annual
Computer Security Applications Conference (ACSAC), Miami, Fl, December 2006.

[2] Paragon for Practical Programming with Information-Flow Control Niklas
Broberg, Bart van Delft and David Sands Asian Symposium on Programming Languages
and Systems (APLAS) 2013, Springer

[3] http://www.cse.chalmers.se/research/group/paragon/?p=Case%20Studies

### 2014-04-25 paper/rebuttal.txt

# is the system general?
#
# true, we can't handle external effects

@@

# is the system general?
#
# true, we can't handle external effects

The reviewers are concerned that our treatment of external effects makes the
work incomplete. We remark that like other IFC systems, external effects can be
handled by internalizing them (manually) into the IFC language. For instance,
JPMail (a secure mail agent) [1] essentially re-implements the primitives with
external effects in Jif (a compiler for IFC in Java). In addition, Paragon [2]
internalizes external effects by wrapping the corresponding primitives to be
IFC-aware [3]. JSFlow [25] manually wraps JavaScript primitives with external
effects. Similarly, as in the XMLHttpRequest used in SWAPI, our technique
amounts to wrapping the "native" unsafe code. While we can extend the language
with a general external effect primitive (e.g., 'out'), we do not think this add
much value, formally or practically. This is because the treatment of external
effects is very much application specific. For instance, the HTTP client in
SWAPI (XMLHttpRequest) and LIO (as used in Hails [22]) both wrap the native code
to make IFC-aware, but the actual label checks differ simply because of the
different setting and attacker models: browser (client) vs. server.  While
important for pushing IFC into practice, we believe that general treatment of
external effects is an open problem and complementary to this work.

Generality and novelty of the system
------------------------------------

# that doesn't make it not real

A reviewer asked if our system really applies to real-world languages,
pointing to our inability to deal with external effects.  It is true
that our framework assumes that the target language must not have
external effects.  However, this is not an unreasonable constraint: in
Section 6, we discussed how real-world languages can be constrained to
achieve this.  Unfortunately, due to space restrictions, we left the
discussion of the mapping to the formalism as informal discussion.

### 2014-04-25 paper/rebuttal.txt

Similarly, there was a comment that this work simply shoe-horned SWAPI
and LIO into a "unified framework".  While our language uses ideas from
LIO and SWAPI, we note that the current (and at the time of the writing)
versions of these systems are using the concepts of this paper. It is
not the case that "the framework didn't come first". For instance, in
LIO [53] (and Breeze [28]) exceptions were originally treated in a rather
complex fashion; as we discuss in the paper, exceptions are internal
effects and thus the security concern becomes trivial; LIO was modified to
adopt this new approach.

As for the first reviewer's concern that the IFC system presented is
simply a rehash of prior work, we claim the approach of dealing with
internal effects and our asynchronous communication primitives is
novel. To our knowledge this is the first language-based dynamic IFC
system to use such asynchronous primitives and work on both concurrent
and sequential schedulers. (While simple, the checks performed by our
asynchronous communication primitives imply a more flexible
system---synchronous primitives effectively impose that the end-points
have the same label.) Moreover, we believe that our formalization
serves as a stepping stone for formal reasoning about IFC OS work.

Extensions
----------

Reviewer 1 asks about the extension section, and whether we actually
worked out these ideas or not. We chose to present the core ideas
separately from extensions for simplicity. However, the IFC language
extensions described in Section 6 have been formally worked out, and
are also part of the JavaScript or Haskell implementation, or both.
W.r.t. the comment about labeled references not being amenable to
Matthews-Findler-style semantics, we note that labeled references
are part of the IFC state and are distinct from the native references
a target language might have. For this reason, there is no conflict
with the approach of Matthews and Findler.

### 2014-04-25 paper/rebuttal.txt

Reviewer 2 asks whether or not our method actually scales in practice,
pointing to our inability to deal with external effects as a mark
against it.  It is true that dealing with external effects is important
for pushing IFC into practice, and our work is not primarily concerned
with addressing this issue.  However, this problem is endemic to all
information flow control systems: for instance, JPMail [1] re-implements
primitives with external effects in Jif; Paragon [2] internalizes
external effects by wrapping the corresponding primitives to be
IFC-aware [3]; JSFlow [25] manually wraps JavaScript primitives with
external effects.  This is not to say that the systems we have
implemented do not deal with external effects: e.g. XMLHttpRequest as
used in SWAPI essential wraps the "native" unsafe code. While we could
have formally modeled these effects with an external effect primitive
(e.g., 'out'), we do not think this add much value, formally or
practically. This is because the treatment of external effects is very
much application specific.

Thus, the generality of our system does not come from a treatment of
external effects; rather, assuming that external effects are taken care
of (Section 6), it comes from our ability to accomodate arbitrarily
complex internal semantics.  For example, our work is directly
applicable to "vanilla" JS (EcmaScript), which does not have any
external effects.  As opposed to existing IFC systems [25] which incur
tremendous overhead, we show that you can build an efficient,
non-intrusive IFC system for JavaScript, or any other language which can
be isolated.

# about shoehorning

### 2014-04-25 paper/rebuttal.txt

Reviewer 2 asks whether or not our method actually scales in practice,
pointing to our inability to deal with external effects as a mark
against it.  It is true that dealing with external effects is important
for pushing IFC into practice, and our work is not primarily concerned
with addressing this issue.  However, this problem is endemic to all
information flow control systems: for instance, JPMail [1] re-implements
primitives with external effects in Jif; Paragon [2] internalizes
external effects by wrapping the corresponding primitives to be
IFC-aware [3]; JSFlow [25] manually wraps JavaScript primitives with
external effects.  This is not to say that the systems we have
implemented do not deal with external effects: e.g. XMLHttpRequest as
used in SWAPI essential wraps the "native" unsafe code. While we could
have formally modeled these effects with an external effect primitive
(e.g., 'out'), we do not think this add much value, formally or
practically. This is because the treatment of external effects is very
much application specific.

Thus, the generality of our system does not come from a treatment of
external effects; rather, assuming that external effects are taken care
of (Section 6), it comes from our ability to accomodate arbitrarily
complex internal semantics.  For example, our work is directly
applicable to "vanilla" JS (EcmaScript), which does not have any
external effects.  As opposed to existing IFC systems [25] which incur
tremendous overhead, we show that you can build an efficient,
non-intrusive IFC system for JavaScript, or any other language which can
be isolated.

It's worth stating that we did not simply shoe-horn SWAPI and LIO into a
"unified framework".  While our language uses ideas from LIO and SWAPI,
we note that the current (and at the time of the writing) versions of
these systems coevolved with the concepts in the paper.  For instance,
in LIO [53] (and Breeze [28]) exceptions were originally treated in a
rather complex fashion. As we discuss in the paper, when you consider
exceptions as part of the internal semantics of the language, the
appropriate semantics for exceptions becomes trivial.  In fact, LIO was
modified to adopt this new approach.

# I haven't fixed this
As for the first reviewer's concern that the IFC system presented is
simply a rehash of prior work, we claim the approach of dealing with
internal effects and our asynchronous communication primitives is
novel. To our knowledge this is the first language-based dynamic IFC
system to use such asynchronous primitives and work on both concurrent
and sequential schedulers. (While simple, the checks performed by our
asynchronous communication primitives imply a more flexible
system---synchronous primitives effectively impose that the end-points
have the same label.) Moreover, we believe that our formalization
serves as a stepping stone for formal reasoning about IFC OS work.

### 2014-04-25 paper/rebuttal.txt

Reviewer 2 asks whether or not our method actually scales in practice,
pointing to our inability to deal with external effects as a mark
against it.  It is true that dealing with external effects is important
for pushing IFC into practice, and our work is not primarily concerned
with addressing this issue.  However, this problem is endemic to all
information flow control systems: for instance, JPMail [1] re-implements
primitives with external effects in Jif; Paragon [2] internalizes
external effects by wrapping the corresponding primitives to be
IFC-aware [3]; JSFlow [25] manually wraps JavaScript primitives with
external effects.  This is not to say that the systems we have
implemented do not deal with external effects: e.g. XMLHttpRequest as
used in SWAPI essential wraps the "native" unsafe code. However, the treatment
of external effects is very much application specific, and finding a
general solution is an open problem.

Thus, the generality of our system does not come from a treatment of
external effects; rather, assuming that external effects are taken care
of (Section 6), it comes from our ability to accommodate arbitrarily
complex internal semantics.  For example, our work is directly
applicable to "vanilla" JavaScript (ECMAScript), which does not have any
external effects.  As opposed to existing IFC systems (e.g., [25]) which incur
tremendous overhead, we show that you can build an efficient,
non-intrusive IFC system for JavaScript, or any other language which can
be isolated.

It's worth stating that we did not simply shoe-horn SWAPI and LIO into a
"unified framework".  While our language uses ideas from LIO and SWAPI,
we note that the current versions of
these systems coevolved with the concepts in the paper.  For instance,
in LIO [53] (and Breeze [28]) exceptions were originally treated in a
rather complex fashion. As we discuss in the paper, when you consider
exceptions as part of the internal semantics of the target language, the
appropriate semantics for exceptions fall out naturally in our framework.
In fact, LIO was modified to adopt this new, simpler approach.

### 2014-04-25 paper/rebuttal.txt

Reviewer 2 asks whether or not our method actually scales in practice,
pointing to our inability to deal with external effects as a mark
against it.  It is true that dealing with external effects is important
for pushing IFC into practice, and our work is not primarily concerned
with addressing this issue.  However, this problem is endemic to all
information flow control systems: for instance, JPMail [A] re-implements
primitives with external effects in Jif; Paragon [B] internalizes
external effects by wrapping the corresponding primitives to be
IFC-aware [C]; JSFlow [25] manually wraps JavaScript primitives with
external effects.  This is not to say that the systems we have
implemented do not deal with external effects: e.g. XMLHttpRequest as
used in SWAPI essential wraps the "native" unsafe code. However, the treatment
of external effects is very much application specific, and finding a
general solution is an open problem.

@@

Reviewer 3 asks about the values sent across channels in SWAPI.  For
simplicity, we require them to be strings in the paper, thought any
structurally cloned object (as well as labeled blobs) are actually
permitted.

Reviewer 1 ask about the soundness of the JS-send rule.  While omitted
in the paper, this rule can be proven to be non-interfering.
Intuitively, for an attacker at level L, the additional premise
evaluates regardless of secrets at a level above L, thus ensuring that
no secrets can be observed.

References
----------

[A] Boniface Hicks, Kiyan Ahmadizadeh, and Patrick McDaniel. Understanding
practical application development in security-typed languages. In 22nd Annual
Computer Security Applications Conference (ACSAC), Miami, Fl, December 2006.

[B] Paragon for Practical Programming with Information-Flow Control Niklas
Broberg, Bart van Delft and David Sands Asian Symposium on Programming Languages
and Systems (APLAS) 2013, Springer

[C] http://www.cse.chalmers.se/research/group/paragon/?p=Case%20Studies

### 2014-04-26 paper/rebuttal.txt

Thus, the generality of our system does not come from a treatment of
external effects; rather, assuming that external effects are taken care
of (Section 6), it comes from our ability to accommodate arbitrarily
complex internal semantics.  For example, our work is directly
applicable to "vanilla" JavaScript (ECMAScript), which does not have any
external effects.  As opposed to existing IFC systems (e.g., [25]) which incur
tremendous overhead, we show that you can build an efficient,
non-intrusive IFC system for JavaScript, or any other language which can
be isolated.

It's worth stating that we did not simply shoe-horn SWAPI and LIO into a
"unified framework".  While our language uses ideas from LIO and SWAPI,
we note that the current versions of
these systems coevolved with the concepts in the paper.  For instance,
in LIO [53] (and Breeze [28]) exceptions were originally treated in a
rather complex fashion. As we discuss in the paper, when you consider
exceptions as part of the internal semantics of the target language, the
appropriate semantics for exceptions fall out naturally in our framework.
In fact, LIO was modified to adopt this new, simpler approach.

Reviewer 1 was concerned that many aspects of our IFC system were simply
rehashes of prior work.  We believe that our core IFC language's support
for both concurrent and sequential scheduling through asynchronous
communication primitives is novel.  (Notice that a primitive which may
block cannot work in a sequential setting).  This is an old idea from IFC
OS work, but formally reasoning about this idea is new.

Reviewer 1 also asks whether or not the ideas in the extension section
were actually worked out.  The IFC language features and external effect
systems mentioned have been implemented for Haskell and JavaScript, and,
in the case of LIO, have had properties formally proven, while the
scheduling policies and type safety extensions are more speculative.
The treatment of mutable references was explicitly called out as
unworkable: we would like to clarify an important distinction between
mutable references in the IFC language and mutable references internally
supported in the target language.  The naive addition of IFC references
results in two *different* types of references: this is a feature,
not a bug, since it avoids the need of adding expensive checks to
existing references which, in all likelihood, are local to an IFC thread.

### 2014-04-26 paper/rebuttal.txt

Thus, the generality of our system does not come from a treatment of
external effects; rather, assuming that external effects are taken care
of (Section 6), it comes from our ability to accommodate arbitrarily
complex internal semantics.  For example, our work is directly
applicable to "vanilla" JavaScript (ECMAScript), which does not have any
external effects.  As opposed to existing IFC systems (e.g., [25]) which incur
tremendous overhead, we show that you can build an efficient,
non-intrusive IFC system for JavaScript, or any other language which can
be isolated.

It's worth stating that we did not simply shoe-horn SWAPI and LIO into a
"unified framework".  While our language uses ideas from LIO and SWAPI,
we note that the current versions of
these systems coevolved with the concepts in the paper.  For instance,
in LIO [53] (and Breeze [28]) exceptions were originally treated in a
rather complex fashion. As we discuss in the paper, when you consider
exceptions as part of the internal semantics of the target language, the
appropriate semantics for exceptions fall out naturally in our framework.
In fact, LIO was modified to adopt this new, simpler approach.

Reviewer 1 was concerned that many aspects of our IFC system were simply
rehashes of prior work.  We believe that our core IFC language's support
for both concurrent and sequential scheduling through asynchronous
communication primitives is novel.  (Notice that a primitive which may
block cannot work in a sequential setting).  This is an old idea from IFC
OS work, but formally reasoning about this idea is new.

Reviewer 1 also asks whether or not the ideas in the extension section
were actually worked out.  The IFC language features and external effect
systems mentioned have been implemented for Haskell and JavaScript, and,
in the case of LIO, have had properties formally proven, while the
scheduling policies and type safety extensions are more speculative.
The treatment of mutable references was explicitly called out as
unworkable: we would like to clarify an important distinction between
mutable references in the IFC language and mutable references internally
supported in the target language.  The naive addition of IFC references
results in two *different* types of references: this is a feature, not a
bug, since it absolves us of the responsibility of integrating the two
semantics.  Furthermore, existing code using old references does not
usually need to communicate over IFC boundaries, so code being written
to take advantage of the new IFC support can be written to explicitly use
IFC references.  This approach of adding features to the core IFC
calculus extends to our other proposed extensions, and their security
proofs are generalizable to our setting in the same way.

### 2014-04-26 paper/rebuttal.txt

Reviewer 2 asks whether or not our method actually scales in practice,
pointing to our inability to deal with external effects as a mark
against it.  It is true that dealing with external effects is
important for pushing IFC into practice, and our work is not primarily
concerned with addressing this issue.  However, this problem is
endemic to all information flow control systems: for instance, JPMail
[A] re-implements primitives with external effects in Jif; Paragon [B]
internalizes external effects by wrapping the corresponding primitives
to be IFC-aware [C]; JSFlow [25.26] manually wraps JavaScript
primitives with external effects.  This is not to say that the systems
we have implemented do not deal with external effects: e.g.
XMLHttpRequest as used in SWAPI essential wraps the "native" unsafe
code. However, the treatment of external effects is very much
application specific, and finding a general solution is an open
problem.

### 2014-04-26 paper/rebuttal.txt

We would like to thank all reviewers for their feedback and suggestions.
We will first reply to high-level comments and then reply to specific
questions in the reviews.

Reviewer 2 asks whether or not our method actually scales in practice,
pointing to our inability to deal with external effects as a mark
against it.  It is true that dealing with external effects is
important for pushing IFC into practice, and our work is not primarily
concerned with addressing this issue.  However, this problem is
endemic to all information flow control systems: for instance, JPMail [A]
re-implements primitives with external effects in Jif; Paragon [B]
internalizes external effects by wrapping the corresponding primitives
to be IFC-aware [C]; JSFlow [25,26] manually wraps JavaScript
primitives with external effects.  This is not to say that the systems
we have implemented do not deal with external effects: e.g.
XMLHttpRequest as used in SWAPI essential wraps the "native" unsafe
code. However, the treatment of external effects is very much
application specific, and finding a general solution is an open
problem.

### 2014-05-09 paper/appendix.tex
Start formalizing some of the extensions.

\appendix
\section{Full Non-Interference Proof}
\label{sec:appendix}

>>>>

\appendix

\section{Formal Extensions}

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | Labeled il ie
    ie  ::= cdots | label ie ie | unlabel ie | labelOf ie
    iE  ::= cdots | label iE ie | unlabel iE | labelOf iE
  \end{code}

  \begin{mathpar}
    \inferrule[I-label]
    {|
      il canFlowTo il'
    |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
    |}
    \and
    \inferrule[I-unlabel]
    {|
      il''=il lub il'
    |}
    {|
      niconf iS id il (unlabel (Labeled il' ie))
      ->
      niconf iS id (il'') ie
    |}
    \and
    \inferrule[I-labelOf]
    {|
    |}
    {|
      niconf iS id il (labelOf (Labeled il' ie))
      ->
      niconf iS id il (il')
    |}
  \end{mathpar}
  \caption{}
  \label{fig:labeled-vals}
  %}
\end{figure}

\begin{figure}
  %{
  %format .->  = "\overset{\alpha}{\hookrightarrow}"
  %format .-/>  = "\not\overset{\alpha}{\hookrightarrow}"
  \begin{code}
    iv  ::= cdots | ial
    ie  ::= cdots | new ie ie | read ie | write ie ie
    iE  ::= cdots | new iE ie | new il iE | read E
                  | write iE ie | write ial iE
  \end{code}

  \begin{mathpar}
    \inferrule[I-new]
    {
      |il canFlowTo il'| \\
      |fresh ia|
    }
    {|
      niconf iS id il (new il' iv)
      ->
      niconf iS id il (iall il')
      |}
    \and
    \inferrule[I-read]
    {|
      il canFlowTo il'
      |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
      |}
    \and
    \inferrule[I-write]
    {|
      il canFlowTo il'
      |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
      |}
    \and
    \inferrule[I-labelOf2]
    {|
      il canFlowTo il'
      |}
    {|
      niconf iS id il (label il' ie)
      ->
      niconf iS id il (Labeled il' ie)
      |}
  \end{mathpar}
  \caption{}
  \label{fig:labeled-refs}
  %}
\end{figure}

\section{Full Non-Interference Proof}
\label{sec:appendix}
